Association between Breast Cancer and Hepatitis C Virus with Age Controlling

### 2022-11-15 manuscript/manuscript.tex
abstract
refs

\begin{abstract}
In Egypt Hepatitus C virus infection is a common problem that often impedes treatment
of Breast Cancer in female patients. While previous work has analyze an associaiton 
between HCV seropositivity and breast cancer diagnosis, this paper will focus on the 
potential confounding of age on the association. We will use Fisher's Exact Test to
estimate the crude estimate of the association and the Mantel-Haenszel method to 
stratify the data between ages. The possible effect of age in the association can
lead to improved care for patients.

@@

\section{Discussion}
\label{sec:discuss}
Based on the analysis, it is evident that for women under the age of 45,
seropositivity and breast cancer are strongly associated. As being HCV 
positive can complicate treatment of cancer, this is critical information.
In Egypt, breast cancer remains the most common form or cancer and high 
levels of hepatitus C continue. This study was retrospective so analysis 
was limited to observing odds ratios and the sample size was quite small.
Thus, future studies should aim to be prospective cohort studies so 
researchers can observe how seropisitivity and breast cancer interact 
over time. 
Additionally, age is just one factor that can affect the associaiton 
between hepatitus C and breast cancer. Future studies should dive 
deeper into more factors such as weight, reproductive history, 
and alcohol consumption. Addiitonally, future studies can explore how 
seropositivity affects tumor size, disease agression, and more. As 
breast cancer is so prevalent in Egypt, further understanding the 
risk factors is becoming even more importnant.

>>>>

\begin{abstract}
In Egypt, Hepatitus C virus infection is a common problem that often impedes treatment
of breast cancer in female patients. While previous work has analyze an associaiton 
between HCV seropositivity and breast cancer diagnosis, this paper will focus on the 
potential confounding of age on the association. We will use Fisher's Exact Test to
estimate the crude estimate of the association and the Mantel-Haenszel method to 
stratify the data between ages. The possible effect of age in the association can
lead to improved care for patients.

@@

\section{Discussion}
\label{sec:discuss}
  Based on the analysis, it is evident that for women under the age of 45,
seropositivity and breast cancer are strongly associated. As being HCV 
positive can complicate treatment of cancer, this is critical information.
In Egypt, breast cancer remains the most common form or cancer and high 
levels of hepatitus C continue. This study was retrospective so analysis 
was limited to observing odds ratios and the sample size was quite small.
Thus, future studies should aim to be prospective cohort studies so 
researchers can observe how seropisitivity and breast cancer interact 
over time. 
  Additionally, age is just one factor that can affect the associaiton 
between hepatitus C and breast cancer. Future studies should dive 
deeper into more factors such as weight, reproductive history, 
and alcohol consumption. Addiitonally, future studies can explore how 
seropositivity affects tumor size, disease agression, and more. As 
breast cancer is so prevalent in Egypt, further understanding the 
risk factors is becoming even more important.

\vspace{4cm}
